Ignition of Fuel Beds by Firebrands

### 2022-04-12 litreview.tex
Updates to introduction

    A significant number of ignition criteria and models have been proposed to predict fuel bed ignition, however no model has provided a general quantitatively accurate prediction of ignition. 
    \section{Current Ignition Models}
        \begin{itemize}
            \item Hot spot theory (Hadden 2011)
            \item Critical mass flux (Nelson 1995)
            \item Energy content of the particle
            \item Numerical methods
            \item Analytic correlations
        \end{itemize}

>>>>

    Another approach that has been used to predict the onset of ignition in fuels is defining the critical mass flux for ignition. The critical mass flux model asserts that if energy is transferred into a fuel in at such a rate or quantity that the mass flux of pyrolysis products release are above the "critical" value ignition will occur~\cite{Nelson1995}. The critical mass flux approach has been primarily considered for the ignition of solid materials such as PMMA~\cite{Rich2007} and wood slabs~\cite{Yashwanth2015, McAllister2013}. In these studies the critical mass flux was well correlated with ignition however, a general model that predicts ignition across materials and experiments is lacking. One shortcoming is the sensitivity to environmental conditions and material properties. In work conducted by McAllister for wooden plates sensitivities to thermal boundary conditions were anticipated to be magnified in the consideration of fuel beds made of particles. Differences in pyrolysis between the materials was also of concern as oxygen availability and boundary layer effects of the particle fuel beds was postulated to have a significant effect~\cite{McAllister2013}.  Numerical studies considering the critical mass flux for a piloted ignition reported that the mass flux at ignition was sensitive to the Damkolher number above the fuel bed~\cite{Dai2013} giving further support of the sensitivity to boundary conditions (i.e., wind near the ignition source). While further study and development of the critical mass flux model may be adjusted to address these sensitivities it also has other shortcomings.

    A significant number of ignition criteria and models have been proposed to predict fuel bed ignition, however no model has provided a general quantitatively accurate prediction of ignition. 
    \section{Current Ignition Models}
        \begin{itemize}
            \item Hot spot theory (Hadden 2011) (Done)
            \item Critical mass flux (Nelson 1995)
            \item Energy content of the particle
            \item Numerical methods
            \item Analytic correlations
        \end{itemize}
